---
title: "Daily Ambience Comparison"
date: "`r format(Sys.Date(),'%b %d, %Y')`"
output: html_document
knit: (function(input, encoding) {
  rmarkdown::render(input,
                    output_dir = "../output")})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE,echo=FALSE,warning = FALSE,message=FALSE)
knitr::opts_chunk$set(fig.dim = c(9, 7))

library(plotly)
library(dplyr)

setwd(file.path("~","Documents","projects","ambience_reports","ambience_comparison"))
amb_dataset = read.csv(file.path("intermediate_data","test.csv"))
#sleep_dataset = fromJSON(file.path("intermediate_data","oura_sleep_2024-08-04T19-54-06.json"),flatten = T)

amb_dataset$reading_dttm = as.POSIXct(amb_dataset$reading_dttm)
amb_dataset = amb_dataset %>% arrange(reading_dttm)

x_lower = as.POSIXct(paste0(format(min(amb_dataset$reading_dttm),"%Y-%m-%d")," 00:00"))
x_upper = as.POSIXct(paste0(format(max(amb_dataset$reading_dttm),"%Y-%m-%d")," 24:00"))

dateList = seq(as.Date(format(x_lower,"%Y-%m-%d")),as.Date(format(x_upper,"%Y-%m-%d")),by="1 day")

```

## Plots {.tabset}

The graphs below below are the results the [ambience database](https://snyderjo.github.io/ambience/).  

The idea is to identify any notable differences between the measurements the pi's in two different room: my bedroom, and the living room.  


### Temperature  

```{r Temperature, echo=FALSE}
fig = plot_ly(data = amb_dataset, x = ~reading_dttm) 

fig = fig %>% add_lines(y = ~temp,color = I("red"), linetype = ~room)
fig = fig %>% layout(
    title = NULL,
    xaxis = list(
      range=c(x_lower,x_upper)
      ,title = "date-time"
      ,rangeslider = list(type = "dateteime")
      ),
    yaxis = list(title = "Temperature (C)"))

fig
```

Some of you might be asking: *Does it really get above 40 (104 degrees Fahrenheit) in your bedroom???*  
No.  The sensor is attached to a raspberry pi, which produces a good amount of heat on its own.  The above data measures temperature with a consistent bias.

### Humidity  

```{r humidity, echo=FALSE}
fig = plot_ly(data = amb_dataset, x = ~reading_dttm) 

fig = fig %>% add_lines(y = ~humidity,color = I("orange"), linetype = ~room)
fig = fig %>% layout(
    title = NULL,
    xaxis = list(
      range=c(x_lower,x_upper)
      ,title = "date-time"
      ,rangeslider = list(type = "dateteime")
      ),
    yaxis = list(title = "Humidity (%)")
    )

fig
```

### Pressure  

```{r pressure, echo=FALSE}
fig = plot_ly(data = amb_dataset, x = ~reading_dttm) 

fig = fig %>% add_lines(y = ~pressure,color = I("green"),linetype = ~room)
fig = fig %>% layout(
    title = NULL,
    xaxis = list(
      range = c(x_lower, x_upper)
      ,title = "date-time"
      ,rangeslider = list(type = "dateteime")
      ),
    yaxis = list(title = "Pressure (mbar)")
    )

fig
```

### Pitch  

```{r pitch, echo=FALSE}
fig = plot_ly(data = amb_dataset, x = ~reading_dttm) 

fig = fig %>% add_lines(y = ~pitch,color = I("blue"), linetype = ~room)
fig = fig %>% layout(
    title = NULL,
    xaxis = list(
      range=c(x_lower,x_upper)
      ,title = "date-time"
      ,rangeslider = list(type = "dateteime")
      ),
    yaxis = list(
      range=c(0,360)
      ,title = "Pitch (degrees)"
      )
    )

fig
```

### Roll  

```{r roll, echo=FALSE}
fig = plot_ly(data = amb_dataset, x = ~reading_dttm) 

fig = fig %>% add_lines(y = ~roll,color = I("blue"), linetype = ~room)
fig = fig %>% layout(
    title = NULL,
    xaxis = list(
      range=c(x_lower,x_upper)
      ,title = "date-time"
      ,rangeslider = list(type = "dateteime")
      ),
    yaxis = list(
      range=c(0,360)
      ,title = "Roll (degrees)"
      )
    )

fig
```

### yaw  

```{r yaw, echo=FALSE}
fig = plot_ly(data = amb_dataset, x = ~reading_dttm) 

fig = fig %>% add_lines(y = ~yaw,color = I("blue"), linetype = ~room)
fig = fig %>% layout(
    title = NULL,
    xaxis = list(
      range=c(x_lower,x_upper)
      ,title = "date-time"
      ,rangeslider = list(type = "dateteime")
      ),
    yaxis = list(
      range=c(0,360)
      ,title = "Yaw (degrees)"
      )
    )

fig
```

### Acceleration [X]  

```{r accel_x, echo=FALSE}
fig = plot_ly(data = amb_dataset, x = ~reading_dttm) 

fig = fig %>% add_lines(y = ~accel_x,color = I("purple"), linetype = ~room)
fig = fig %>% layout(
    title = NULL,
    xaxis = list(
      range=c(x_lower,x_upper)
      ,title = "date-time"
      ,rangeslider = list(type = "dateteime")
      ),
    yaxis = list(title = "Acceleration [X] (G's)")
    )

fig
```

### Acceleration [Y]  

```{r accel_y, echo=FALSE}
fig = plot_ly(data = amb_dataset, x = ~reading_dttm) 

fig = fig %>% add_lines(y = ~accel_y,color = I("purple"), linetype = ~room)
fig = fig %>% layout(
    title = NULL,
    xaxis = list(
      range=c(x_lower,x_upper)
      ,title = "date-time"
      ,rangeslider = list(type = "dateteime")
      ),
    yaxis = list(title = "Acceleration [Y] (G's)")
    )

fig
```


### Acceleration [z]  

```{r accel_z, echo=FALSE}
fig = plot_ly(data = amb_dataset, x = ~reading_dttm) 

fig = fig %>% add_lines(y = ~accel_z,color = I("purple"), linetype = ~room)
fig = fig %>% layout(
    title = NULL,
    xaxis = list(
      range=c(x_lower,x_upper)
      ,title = "date-time"
      ,rangeslider = list(type = "dateteime")
      ),
    yaxis = list(title = "Acceleration [Z] (G's)")
    )

fig
```

Note: This should be measuring the vertical acceleration, i.e. gravity.  
Unless something changes, there's notable variability around the value of 1 in the living room.  The Bedroom value holds steady around .985 G's.  
Taken at face value, it means that  
1. Gravity effect is slightly lesser in my bedroom than in the rest of the world, and  
2. Gravity's value occasionally jumps .6 G's in my living room.  
I'll chalk these differences up to measurement error.  

## A couple of notes:


* What gives with the delay between the date this report is rendered vs. what is displayed below?  
  + If the data were immediate, it would be entirely too clear when I was out of town--information I'm not keen to share.  
* There are notable gaps in data.  Why?  
   + Some days the [DAG](https://airflow.apache.org/docs/apache-airflow/1.10.9/concepts.html) fails for no discernible reason--I invite you to take it up with Apache.  
   + Lacking a power outage, these tiny computers are constantly running.  They are prone to outages--I once neglected to note a pi was not recording for several weeks.

